\author{
SPACEHOLDER ONLY -- The TOTEM Collaboration\\
G.~Antchev\thanksInst{1}
\and P.~Aspell\inst{8}
\and I.~Atanassov\inst{8}\thanksInst{1}
\and V.~Avati\inst{8}
\and J.~Baechler\inst{8}
\and V.~Berardi\inst{5b,5a}
\and M.~Berretti\inst{7b}
\and E.~Bossini\inst{7b}
\and M.~Bozzo\inst{6b,6a}
\and P.~Brogi\inst{7b}
\and E.~Br\"{u}cken\inst{3a,3b}
\and A.~Buzzo\inst{6a}
\and F.~S.~Cafagna\inst{5a}
\and M.~Calicchio\inst{5b,5a}
\and M.~G.~Catanesi\inst{5a}
\and C.~Covault\inst{9}
\and M.~Csan\'{a}d\inst{4}\thanksInst{5}
\and T.~Cs\"{o}rg\H{o}\inst{4}
\and M.~Deile\inst{8}
\and K.~Eggert\inst{9}
\and V.~Eremin\thanksInst{2}
\and R.~Ferretti\inst{6a,6b}
\and F.~Ferro\inst{6a}
\and A. Fiergolski\thanksInst{3}
\and F.~Garcia\inst{3a}
\and S.~Giani\inst{8}
\and V.~Greco\inst{7b,8}
\and L.~Grzanka\inst{8}\thanksInst{4}
\and J.~Heino\inst{3a}
\and T.~Hilden\inst{3a,3b}
\and R.~A.~Intonti\inst{5a}
\and J.~Ka\v{s}par\inst{1a,8}
\and J.~Kopal\inst{1a,8}
\and V.~Kundr\'{a}t\inst{1a}
\and K.~Kurvinen\inst{3a}
\and S.~Lami\inst{7a}
\and G.~Latino\inst{7b}
\and R.~Lauhakangas\inst{3a}
\and T.~Leszko\thanksInst{3}
\and E.~Lippmaa\inst{2}
\and M.~Lokaj\'{\i}\v{c}ek\inst{1a}
\and M.~Lo~Vetere\inst{6b,6a}
\and F.~Lucas~Rodr\'{i}guez\inst{8}
\and M.~Macr\'{\i}\inst{6a}
\and T.~M\"aki\inst{3a}
\and A.~Mercadante\inst{5b,5a}
\and N.~Minafra\inst{8} 
\and S.~Minutoli\inst{6a}
\and F.~Nemes\inst{4}\thanksInst{5}
\and H.~Niewiadomski\inst{8}
\and E.~Oliveri\inst{7b}
\and F.~Oljemark\inst{3a,3b}
\and R.~Orava\inst{3a,3b}
\and M.~Oriunno\inst{8}\thanksInst{6}
\and K.~\"{O}sterberg\inst{3a,3b}
\and P.~Palazzi\inst{7b}
\and J.~Proch\'{a}zka\inst{1a}
\and M.~Quinto\inst{5a}
\and E.~Radermacher\inst{8}
\and E.~Radicioni\inst{5a}
\and F.~Ravotti\inst{8}
\and E.~Robutti\inst{6a}
\and L.~Ropelewski\inst{8}
\and G.~Ruggiero\inst{8}
\and H.~Saarikko\inst{3a,3b}
\and A.~Santroni\inst{6b,6a}
\and A.~Scribano\inst{7b}
\and J.~Smajek\inst{8}
\and W.~Snoeys\inst{8}
\and J.~Sziklai\inst{4}
\and C.~Taylor\inst{9}
\and N.~Turini\inst{7b}
\and V.~Vacek\inst{1b}
\and M.~V\'itek\inst{1b}
\and J.~Welti\inst{3a,3b}
\and J.~Whitmore\inst{10}
}

\shortauthor{The TOTEM Collaboration (G.~Antchev \etal)}

\institute{
\inst{1a}{Institute of Physics of the Academy of Sciences of the Czech Republic, Praha, Czech Republic.}\\
\inst{1b}{Czech Technical University, Praha, Czech Republic.}\\
\inst{2} {National Institute of Chemical Physics and Biophysics NICPB, Tallinn, Estonia.}\\
\inst{3a}{Helsinki Institute of Physics, Finland.}\\
\inst{3b}{Department of Physics, University of Helsinki, Finland.}\\
\inst{4} {MTA Wigner Research Center, RMKI, Budapest, Hungary.}\\
\inst{5a}{INFN Sezione di Bari, Italy.}\\
\inst{5b}{Dipartimento Interateneo di Fisica di Bari, Italy.}\\
\inst{6a}{Sezione INFN, Genova, Italy.}\\
\inst{6b}{Universit\`{a} degli Studi di Genova, Italy.}\\
\inst{7a}{INFN Sezione di Pisa, Italy.}\\
\inst{7b}{Universit\`{a} degli Studi di Siena and Gruppo Collegato INFN di Siena, Italy.}\\
\inst{8} {CERN, Geneva, Switzerland.}\\
\inst{9} {Case Western Reserve University, Dept. of Physics, Cleveland, OH, USA.}\\
\inst{10}{Penn State University, Dept.~of Physics, University Park, PA, USA.}\\
%
\thanksRef{1}{INRNE-BAS, Institute for Nuclear Research and Nuclear Energy, Bulgarian Academy of Sciences, Sofia, Bulgaria.}
\thanksRef{2}{Ioffe Physical -- Technical Institute of Russian Academy of Sciences.}
\thanksRef{3}{Warsaw University of Technology, Poland.}
\thanksRef{4}{Institute of Nuclear Physics, Polish Academy of Science, Cracow, Poland.}
\thanksRef{5}{Department of Atomic Physics, E\"otv\"os University, Hungary.}
\thanksRef{6}{SLAC National Accelerator Laboratory, Stanford CA, USA.}
}

\def\thanksInst#1{\unskip\footnotemark[#1]}

\bgroup
\catcode`\@=11

\gdef\thanksRef#1#2{%
    \protected@xdef\@thanks{\@thanks\protect\footnotetext[#1]{#2}}%
}
\egroup

